---
title: "p8105_hw6_lh3109"
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
```

# Problem 1

## Propose a regression model
### Load and tidy data
```{r, message=FALSE}
bw_df = 
  #import data
  read_csv("./data/birthweight.csv") %>% 
  #remove possible na values
  drop_na() %>% 
  #factor appropriate numeric variables
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
```
This data set contains 4342 observations with 22 variables. It does not contains NA values.

### Select predictors
```{r}
#test model by considering all variables as predictors
fit_test = lm(bwt ~ . , data = bw_df)

#summry results and look for statistically significant predictors of bwt
summary(fit_test)
```

### Fit model
Consider birthweight as an outcome that depend on the predictors that are statistically significant
```{r}
#fit the model
fit = lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + parity + smoken, data = bw_df)

#check the results
summary(fit)
```

### Plot residuals vs. fitted values
```{r}
bw_df %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", se = FALSE, formula = y ~ x) +
  labs(title = "Model Residuals vs. Fitted Values",
       x = "Fitted Values",
       y = "Residuals")
```
As shown in the plot, with fitted value below 2000 or above 4000, the residuals do not "bounce randomly" around the 0 line, suggesting that the data point in this range do not fall on the estimated regression line. This model is not optimal for data outside of the 2000-4000 range for fitted values. However, when fitted values are around 3000, many data points have residuals equals to 0, showing that they falls directly on the estimated regression line, and the model predictions are correct. 


## Compare the model with two others


# Prolem 2

