---
title: "p8105_hw6_lh3109"
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
```

# Problem 1

## Propose a regression model
### Load and tidy data
```{r, message=FALSE}
bw_df = 
  #import data
  read_csv("./data/birthweight.csv") %>% 
  #remove possible na values
  drop_na() %>% 
  #factor appropriate numeric variables
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
```
This data set contains 4342 observations with 22 variables. It does not contains NA values.

### Variable selection
```{r}
#test model by considering all variables as predictors
mult_fit = lm(bwt ~ . , data = bw_df)

#using stepwise backward function to select predictors
step(mult_fit, direction = 'backward')
```

### Fit model
Apply the selected predictors to the model 
```{r}
#fit the model
fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = bw_df)

#check the results
summary(fit)
```

### Plot residuals vs. fitted values
```{r}
bw_df %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", se = FALSE, formula = y ~ x) +
  labs(title = "Model Residuals vs. Fitted Values",
       x = "Fitted Values",
       y = "Residuals")
```
As shown in the plot, with fitted value below 2000 or above 4000, the residuals do not bounce randomly around the 0 line, suggesting that the data point in this range do not fall on the estimated regression line. This model is not optimal for data outside of the 2000-4000 range for fitted values and there are many outliers However, when fitted values are around 3000, many data points have residuals equals to 0 and they falls directly on the estimated regression line. 


## Compare the model with two others


# Prolem 2

